NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-09-30 ms_nihao_budget.tex
rephase the conclusion to explain the definition of R_bar

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter
  ratio,  inside the virial radius, than the cosmic baryon fraction
  (Fig.~\ref{fig:budget}).

\item Lower mass haloes have lost a larger fraction of their baryons,
  even though they convert a much lower fraction of the baryons into
  stars (Fig.~\ref{fig:budget}).  {\bf Similar trends are found by
    other recent simulations \citep{Christensen16,Voort16} using
    different codes (Fig.~\ref{fig:fire_com})}.

\item {\bf The missing baryons have been expelled well beyond the
  virial radius, $R_{200}$, (Fig.~\ref{fig:rps}). Relative to the
  virial radius, the baryons in the amount of fiducial baryonic mass 
  within the virial radiusare expelled to smaller radii in more
  massive haloes: $\Rbar \sim 5 R_{200}$ for $M_{200}=10^{10}\Msun$ and
  $\Rbar \sim 2 R_{200}$ for $M_{200}=10^{12}\Msun$
  (Fig.~\ref{fig:missvr}).}

>>>>

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter
  ratio,  inside the virial radius, than the cosmic baryon fraction
  (Fig.~\ref{fig:budget}). {\bf We refer to the cosmic baryon fraction associated 
  with each dark matter halo as the fiducial baryons.}

\item Lower mass haloes are missing a larger fraction of their {\bf fiducial} baryons,
  even though they convert a much lower fraction of the baryons into
  stars (Fig.~\ref{fig:budget}).  {\bf Similar trends are found by
    other recent simulations \citep{Christensen16,Voort16} using
    different codes (Fig.~\ref{fig:fire_com})}.

\item {\bf The missing baryons have been expelled well beyond the
  virial radius, $R_{200}$, (Fig.~\ref{fig:rps}). Relative to the
  virial radius, the baryons are expelled to smaller radii in more
  massive haloes: $\Rbar \sim 5 R_{200}$ for $M_{200}=10^{10}\Msun$ and
  $\Rbar \sim 2 R_{200}$ for $M_{200}=10^{12}\Msun$
  (Fig.~\ref{fig:missvr}).}
